---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data

1. Load the data (i.e. read.csv())

2. Process/transform the data (if necessary) into a format suitable for your analysis

```{r, echo=TRUE}
setwd("C:/A_R/5-ReproRes/RepData_PeerAssessment1")

activity <- read.table(file = "activity.csv", header = TRUE, sep = ",")

```

## What is mean total number of steps taken per day?

For this part of the assignment, you can ignore the missing values in the dataset.

1. Make a histogram of the total number of steps taken each day
t
2. Calculate and report the mean and median total number of steps taken per day

```{r, echo=TRUE}

install.packages("lattice")
library("lattice", lib.loc="~/R/win-library/3.1")

activity$DateTime <- as.POSIXct(with(activity, paste(date, paste(interval %/% 100, interval %% 100, sep=":"))),
    format="%Y-%m-%d %H:%M",tz="")

AddSteps <- setNames(aggregate(steps~as.Date(date), activity, sum, na.rm = TRUE), c("date","steps"))

xaxis <- seq(1, nrow(AddSteps), by = 6)

okscale <- list(x = list(rot = 45, cex = 1.0, labels = format(AddSteps$date, "%d-%b-%Y")[xaxis], at = xaxis))

barchart(date ~ steps, data = AddSteps, main = "Steps/Day", ylab = "Steps", xlab = "Date", scales = okscale, horizontal = F)

paste("mean:", mean(AddSteps$steps))
paste("median:", median(AddSteps$steps))

```

## What is the average daily activity pattern?


```{r, echo=TRUE}



```


## Imputing missing values


```{r, echo=TRUE}

```


## Are there differences in activity patterns between weekdays and weekends?


```{r, echo=TRUE}

```

